Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-24 VMCAI-revised-version/final.tex
Adding table of results

>>>>

\begin{center}
\resizebox{\textwidth}{!}{
\begin{tabular}{ | l | c | c | c | r |}
\hline   \ 
		& $\Safe = {\uparrow \Safe}$~ 
		 & $\Safe = {\downarrow \Safe}$~ 
 \\ \hline
   \multirow{3}{*}{RP} 
  	& WBTS (post-ideal-effective) Thm~\ref{down-up}
   		 & Downard-WSTS (pred*-basis-effective) Thm~\ref{up-down} \\ 
~	& WBTS (pred-basis-effective) Thm~\ref{xxx}
		& VASS \\\cline{2-3}
~	& WSTS (post-effective) Prop~\ref{indec WSTS} & WSTS (pred-basis-effective) Prop~\ref{indec WSTS with dcs}    \\ \hline
   \multirow{3}{*}{BRP} 
  	& WBTS (post-ideal-effective) Thm~\ref{down-up}
   		 & ? \\ 
~	& WBTS (pred-basis-effective) Thm~\ref{xxx}
		& (VASS ici aussi) \\\cline{2-3}
~	& ? & ?    \\ \hline
   \multirow{3}{*}{kRP} 
 	& WBTS (post-ideal-effective) Thm~\ref{down-up} 
   		 & ? \\ 
~	& WBTS (pred-basis-effective) Thm~\ref{xxx}
		& (VASS ici aussi) \\\cline{2-3}
~	& ? & ?    \\ \hline

   \multirow{2}{*}{sRP} 
  	& WBTS (post-ideal-effective) Thm~\ref{post srp}
   		 & WSTS (downard + upward) Thm~9 \\ \cline{2-3}
~	& WSTS (pred-...) Prop~\ref{srp up down} & WSTS (pred-basis + ??) Prop~\ref{srp up down}    \\ \hline
   \multirow{2}{*}{BsRP} 
  	& WBTS (pred + post*-ideal-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & WSTS (d+up) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS (pred-...) Prop~\ref{srp up down} & ?    \\ \hline
   \multirow{2}{*}{ksRP} 
  	& WBTS (pred + post*-ideal-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & WSTS (d+up) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS (pred-...) Prop~\ref{srp up down} & ?    \\ \hline

 \end{tabular}
  }
\end{center}
